### 2017-04-11 paper/oopsla17-submission/conclusion.tex
minor conclusion

We have presented a new data-driven approach to localizing type errors,
using machine learning to assign blame based on previously seen novice
mistakes.
%
We translate ill-typed programs into sets of feature vectors, predict
for each sub-expression whether it should be blamed, rank the
predictions based on the model's confidence, and select the top three
blame assignments to present to the user.
%
We represent expressions solely by their syntactic class and type, and
those of their parent and children.
%
We have evaluated our approach with five different learning algorithms
on a suite of over 4,500 student programs, and found that all of our
models outperform the state of the art, by up to a 16\% margin.
%

>>>>

We have presented a new data-driven approach to localizing type errors,
using machine learning to assign blame based on previously seen novice
mistakes.
%
We translate ill-typed programs into sets of feature vectors, predict
for each sub-expression whether it should be blamed, rank the
predictions based on the model's confidence, and select the top three
blame assignments to present to the user.
%
We represent expressions solely by their syntactic class and type, and
those of their parent and children.
%
We have evaluated our approach with five different classifiers
on a suite of over 4,500 student programs, and found that all of our
models outperform the state of the art, by up to a 16\% margin.
%
We are particularly excited that our classifiers can be trained on a
modest amount of data, \eg a single course's worth, and envision a
future where each course has a model of its students' errors.
